Copyright

### 2025-03-05 copyright.qmd
Prefer images in high res

You can now download the image and move it to your project folder (maybe call it `penguin.jpg`).
In your manuscript file, find the line that says "add image here", remove it,
and add the image instead, including proper attribution.

>>>>

You can now download the image[^image-resolution]
and move it to your project folder (maybe call it `penguin.jpg`).
In your manuscript file, find the line that says "add image here", remove it,
and add the image instead, including proper attribution.

[^image-resolution]: If you are unsure which image resolution (size) is required,
just download it in the largest possible resolution so it can be printed.
